Fitness tracking reveals task-specific associations between memory, mental health, and physical activity

### 2022-07-17 paper/main.tex
finished complete pass through edits of main text, supplement, and response letter

We also found reliable correlations between participants' fitness and
demographic measures and their behaviors in different tasks
(for a complete report, see Fig.~\allCorr).  For example, recent
low-to-moderate-intensity (``fat burn'') 
cardiovascular activity was positively
correlated with immediate ($r = 0.38, p = 0.03$) and delayed ($r =
0.38, p = 0.029$) recall performance on the naturalistic
memory task.  Recent increases in moderate-intensity (``cardio'')
activity over the prior 7 days (relative to the preceding 30 days) was
also positively correlated with immediate naturalistic recall
performance ($r =
0.48, p = 0.003$) and immediate recall performance on the foreign language
flashcards task ($r = 0.43, p = 0.048$).  Recent high-intensity
(``peak'') activity was positively correlated with performance on the
spatial learning task ($r = 0.34, p < 0.0001$), as were recent increases
in high-intensity activity (prior 7 days versus preceding 30 days; $r
= 0.41, p = 0.01$).  Mental health indicators, such as self-reported
stress levels and medications were also associated with differences in
memory (Figs.~\ref{fig:corr_summaries}, \allCorr).  For example, self-reported stress levels at the time of test
were negatively correlated with performance on the delayed memory test
for the foreign language flashcards task ($r = -0.29, p = 0.038$),
whereas participants who were medicated for anxiety and depression
tended to perform slightly (but reliably) \textit{better} on the immediate memory test for the
foreign language flashcards task ($r = 0.11, p < 0.0001$).

>>>>

We also found reliable correlations between participants' fitness and
demographic measures and their behaviors in different tasks
(Fig.~\ref{fig:corr_summaries}; for a complete report, see Fig.~\allCorr).
For example, recent low-to-moderate-intensity (``fat burn'')
cardiovascular activity was positively correlated with immediate
($r = 0.44, p = 0.001$) and delayed ($r = 0.38, p = 0.031$) recall
performance on the naturalistic memory task.  Recent sedentary
(``out-of-range'') cariovascular activity was negatively correlated
with performance on the spatial learning task
($r = -0.31, p = 0.042$), whereas recent high intensity (``peak'')
activity was positively correlated with performance on the spatial
learning task ($r = 0.34, p = 0.0002$).  Mental health indicators,
such as self-reported stress levels and medications were also
associated with differences in memory
(Figs.~\ref{fig:corr_summaries}a, \allCorr).  For example,
self-reported stress levels at the time of test were negatively
correlated with performance on the delayed memory test for the foreign
language flashcards task ($r = -0.29, p = 0.038$), whereas
participants who were medicated for anxiety and depression tended to
perform slightly (but reliably) \textit{better} on the immediate
memory test for the foreign language flashcards task
($r = 0.11, p < 0.0001$).  Mental health indicators were also
correlated with several fitness measures
(Fig.~\ref{fig:corr_summaries}c).  For example, participants with
higher resting heart rates were less likely to be hypothyroid ($r =
-0.33, p < 0.0001$).  Participants who engaged in more low-intensity
(``light'') activity tended to be less anxious and depressed ($r =
-0.12, p = 0.03$), whereas participants who engaged in more
high-intensity activity tended to report higher levels of current ($r
= 0.15, p = 0.027$) and typical ($r = 0.21, p = 0.012$) stress.
